A Fully Decentralized Infrastructure for Subscription-based IoT Data Trading

### 2020-07-07 paper.tex
Fix grammar

The details of data product, such as data price, MAM channel/endpoint ID and the length of data stream are listed on the Product Contract. As regard to the encryption key of data product, data providers send the hash digest of encryption key to a broker, who will then sign it and written on the Product Contract. This provides an approach for data consumers to verify the encryption key that avoid data providers dishonest toward data consumers with a wrong one. The workflow is shown in Fig.~\ref{fig:launching_product} and the certification codes in Product Contract is in Listing.~\ref{lst:key_certification}. Finally, the data product is launched and data providers can start uploading data.

>>>>

The details of data product, such as data price, MAM channel/endpoint ID and the length of data stream are listed on the Product Contract. As regard to the encryption key of data product, data providers send the hash digest of encryption key to a broker, who will then sign it and write it on the Product Contract. This provides an approach for data consumers to verify the encryption key that avoid data providers dishonest toward data consumers with a wrong one. The workflow is shown in Fig.~\ref{fig:launching_product} and the certification codes in Product Contract is in Listing.~\ref{lst:key_certification}. Finally, the data product is launched and data providers can start uploading data.
